\mutagen: Coverage-Guided, Property-Based Testing using Exhaustive Structure-Preserving Mutations

### 2021-09-03 papers/icse22/main.tex
Pass over conclusion

\begin{verbatim}
genTree(sz) =
  if sz == 0 then do x <- genInt ; return (Leaf x)
  else oneof [ do i <- genInt ; return (Leaf i)
             , do l <- genTree(sz-1) ;
                  x <- genInt        ;
                  r <- genTree(sz-1) ;
                  return (Branch l x r) ]
\end{verbatim}

@@

We presented \mutagen, a coverage-guided, property-based testing framework
written in Haskell.
%
%% Inspired by exhaustive bounded testing tools,
%
Our tool extends the CGPT approach introduced by
\citeauthor{lampropoulos2019coverage} with an exhaustive mutation mechanism that
generates every possible mutant for each interesting test case, and schedules it
to be tested exactly once.

>>>>

\begin{verbatim}
genTree(sz) =
  if sz == 0 then do x <- genInt ; return (Leaf x)
  else oneof [ do x <- genInt ; return (Leaf x)
             , do l <- genTree(sz-1) ;
                  x <- genInt        ;
                  r <- genTree(sz-1) ;
                  return (Branch l x r) ]
\end{verbatim}

@@

We presented \mutagen, a coverage-guided, property-based testing framework.
%written in Haskell.
%
%% Inspired by exhaustive bounded testing tools,
%
Our tool extends the CGPT approach
%introduced by
%\citeauthor{lampropoulos2019coverage}
with an exhaustive mutation mechanism that generates every possible mutant for
each interesting test case, and schedules it to be tested exactly once.
